Evolution of Flare Rates in GKM Stars Younger than 300 Myr

### 2023-11-17 src/tex/ms.tex
add teff hist

% Title
\title{Flare Rates and Rotation Periods of 5700 Stars Younger than 300 Myr}

@@

\begin{figure}[ht!]
    \script{flare_distribution.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/flare_distribution.pdf}
        \caption{
            High level summary of the demographics of flares in our sample. Top:
            The number of flares identified compared to the number of stars in
            each nearby young moving group, cluster, or association. A one-to-one
            relationship is expected. Middle: The distribution measured TESS energies
            and equivalent durations of flares in our sample, colored by the probability
            of the flare as identified with \texttt{steela}. Bottom: Same as the
            middle plot, except colored by the $T_\textrm{eff}$ [K] of the star.
            We limit our sample to stars with $T_\textrm{eff} \leq 6000$\,K.
        }
        \label{fig:flare_distribution}
    \end{centering}
\end{figure}

>>>>

% Title
\title{Evolution of Flare Rates in GKM Stars Younger than 300 Myr}

@@

\begin{figure}[ht!]
    \script{flare_distribution.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/flare_distribution.pdf}
        \caption{
            High level summary of the demographics of flares in our sample. Top:
            The number of flares identified compared to the number of stars in
            each nearby young moving group, cluster, or association. A one-to-one
            relationship is expected. Middle: The distribution measured TESS energies
            and equivalent durations of flares in our sample, colored by the probability
            of the flare as identified with \texttt{stella}. Bottom: Same as the
            middle plot, except colored by the $T_\textrm{eff}$ [K] of the star.
            We limit our sample to stars with $T_\textrm{eff} \leq 6000$\,K.
        }
        \label{fig:flare_distribution}
    \end{centering}
\end{figure}
